%=============================================================================%
% The copyright page
% exact licence to be discussed, there might be some addition saying that code
% and code snippets are EPL
%=============================================================================%

\vfill
\begin{footnotesize}
\setlength{\parindent}{0pt}
This book is available as a free download from TBD \\[1cm]

Copyright \copyright~2012 by Matthias Zimmermann, BSI Business Systems Integration AG. \\ \url{www.bsiag.com} 
\vspace{5mm}

The contents of this book are protected under Creative Commons Attribution-ShareAlike 3.0 Unported license.
Exact final licence to be discussed. Whatever the choice, requirements include
\begin{itemize}
  \item simple and free to consume
  \item simple and free to distribute/rehash
  \item simple and free to contribute
\end{itemize} 

There might be some addition saying that both examples and code snippets are EPL

\vspace{5mm}

\emph{You are free:}
\begin{description}
  \item[to Share] \,---\, to copy, distribute and transmit the work
  \item[to Remix] \,---\, to adapt the work
\end{description} 
\vspace{5mm}

\emph{Under the following conditions:}
\begin{description}
  \item[Attribution.] You must attribute the work in the manner specified by the author or licensor (but not in any way that suggests that they endorse you or your use of the work).
  \item[Share Alike.] If you alter, transform, or build upon this work, you may distribute the resulting work only under the same, similar or a compatible license.
\end{description}

\begin{itemize}
  \item For any reuse or distribution, you must make clear to others the license terms of this work. The best way to do this is with a link to this web page: \\
  \url{www.creativecommons.org/licenses/by-sa/3.0/}
  \item Any of the above conditions can be waived if you get permission from the copyright holder.
  \item Nothing in this license impairs or restricts the author's moral rights.
\end{itemize}

%-----------------------------------------------------------------------------%
% isbn, published by etc. goes here once it applies

\end{footnotesize}
\vfill

%=============================================================================%
