% =========================================================================== %
% Preface
% please make sure that this fits into two pages (max)
% =========================================================================== %

\ifx\wholebook\relax\else
  \documentclass[a4paper,10pt,twoside]{book}
  \input{../common}
  \pagestyle{headings}
  \graphicspath{{figures/} {../figures/}}
  \begin{document}
  \sloppy
\fi


% --------------------------------------------------------------------------- %
\chapter{Preface}

% this chapter already contains the planned content. 
% is not intended for contributions.
% nevertheless: improvements regarding spelling, style, etc are welcome

% --------------------------------------------------------------------------- %
\section*{Who should read this Book?}

\begin{itemize}
\item You want to build a multi-user mobile application.
\item You have to build a Java based business application. 
\item You need to decide on the IT strategy of your organisation
\item You would like to show off the great library you have built but have hardly time for the good looking UI that it deserves
\end{itemize}

\noindent If any of the above scenarios is relevant in your situation, you might want to consider \secref{whatshouldiread} on what to read and in which order.

% --------------------------------------------------------------------------- %
\section*{This Book is Open and Free}

\begin{itemize}
\item Access is simple. 
To download the book you do not need to register or pay subscription fees. 
To cater for individual preferences the book is available in various formats. 
Eventually, there should also be a printed version. And translations.

\item Reuse/rehash is simple. 
This book is released under the Creative Commons (CC-BY) license. 
See~\appref{cclicence} for details.

\item Contribution is simple. 
That's why the source files are all available on Github and we maintain a continuous integration (CI) infrastructure for building the book. 
The necessary information to help you to contribute is available on the Scout
wiki.\footnote{The Scout book \url{http://wiki.eclipse.org/Scout/Book/}}
\end{itemize}

\noindent In short, you are allowed to freely use, share and adapt this book, as long as you respect the conditions of the license mentioned above.

\newpage

% --------------------------------------------------------------------------- %
\section*{The Scout Community}

The community around Scout is its most valuable asset.
It is active, growing and friendly.
This is why it deserves to be mentioned right here.
The Scout forum\footnote{Scout forum \url{http://www.eclipse.org/forums/eclipse.scout}} is the central place for the Scout community to share ideas, ask questions and get help. 
Other, less interactive community resources are the Scout wiki 
pages\footnote{Scout wiki \url{http://wiki.eclipse.org/scout}}, the Scout 
homepage\footnote{Scout homepage \url{http://www.eclipse.org/scout}}, 
the blog\footnote{Scout blog \url{http://www.bsiag.com/scout}}, and 
twitter\footnote{Scout twitter \url{http://twitter.com/EclipseScout}}.

The simplest way to become a community member yourself is to start with downloading
Scout from the Eclipse download site\footnote{Scout download \url{http://www.eclipse.org/downloads/}}, 
installing the software as described in \appref{install_scout}, and continue reading here.

% --------------------------------------------------------------------------- %
\section*{The Current State}

With the Eclipse Kepler release a first (and still rough) version of the Eclipse Scout book is available. 
In its current state, this book provides a reasonable introduction into the Eclipse Scout framework. 
To allow for external contributions from the Scout community, the book's setup has been designed to invite collaboration\footnote{
The books technical setup and contributing work flow is described in the Scout wiki: \url{http://wiki.eclipse.org/Scout/Book/}.
} 

Over time -- and with each new Scout release -- this book is intened to be updated and extended to cover more aspects with every release.

% --------------------------------------------------------------------------- %
\section*{Thanks!}

Many ideas regarding various aspects of this book, such the book's setup, were copied from freely available resources on the web. 
Significant impact had ''Pharo by Example''\footnote{''Pharo by Example'' \url{http://pharobyexample.org/}}.

Last but not least, we thank BSI Business Systems Integration 
AG\footnote{BSI Business Systems Integration AG \url{http://www.bsiag.com/}} for its contribution of Eclipse Scout to the open source community.
For its dedication to open standards and the support to further evolve Scout and its growing community.

% --------------------------------------------------------------------------- %

\ifx\wholebook\relax\else
   \input{../bibliography}
   \end{document}
\fi

% =========================================================================== %
